Detecting Facial Expressions in Video Stills from Professional Tennis Matches

### 2017-09-21 paper/paper.Rmd
added new latex table for accessories

\begin{table}[htp]
%\parbox{.5\linewidth}{
\caption{Counts of captures of different APIs against manually tagged faces.}
\label{tab:facecounts}
\centering
\begin{tabular}{ccccccc}
\cline{1-3}\cline{5-7} 
\multicolumn{3}{c}{Animetrics}&&\multicolumn{3}{c}{Google}\\\cline{1-3}\cline{5-7}
Manual & Face & No Face & & Manual & Face & No Face\\ 
%heading
\cline{1-3}\cline{5-7} 
Face & 434 & 1861 & & Face & 1319 & 976\\
NoFace &527 & 787 & & NoFace &638 & 676 \\\cline{1-3}\cline{5-7}
\end{tabular}
\\[1.5ex]
\begin{tabular}{ccccccc}
\cline{1-3}\cline{5-7} 
\multicolumn{3}{c}{Microsoft}&&\multicolumn{3}{c}{Skybiometry}\\\cline{1-3}\cline{5-7}
Manual & Face & No Face & & Manual & Face & No Face\\ 
%heading
\cline{1-3}\cline{5-7} 
Face & 565 & 1730 & & Face & 493 & 1802\\
No Face &505 & 809 & & No Face &512 & 802 \\\cline{1-3}\cline{5-7}
\end{tabular}
\end{table}

\begin{table}[h]
\parbox{.5\linewidth}{
\centering
\begin{tabular}{ccc}
\hline
Manual & Face & No Face\\ [0.5ex] 
%heading
\hline
Face & 565 & 1730 \\
NoFace &505 & 809 \\ \hline
\end{tabular}
\caption{Microsoft}
}
\hfill
\parbox{.5\linewidth}{
\centering
\begin{tabular}{ccc}
\hline  
Manual & Face & No Face\\ [0.5ex] 
%heading
\hline 
Face & 493 & 1802 \\
NoFace &512 & 802 \\ \hline
\end{tabular}
\caption{Skybiometry}
}
\end{table}

Each table above considers the individual faces found in the set.
The upper left quadrant of tables shows the faces found manually and by each API. The ideal set would have majority of faces found belong to this category. 
Table \@ref(tab:facecounts), the comparison of Animetrics and Manually annotated faces, gives the lowest amount in this regard. Table 5, Google, found the largest amount of faces that matched those manually annotated.

Visual inspection showed that the `r amin %>% filter(type=="Google",!matchesManual) %>% nrow()` potential faces noted in Table 5, that were found by Google but not found manually were actually faces, however they were not all of players. Some of these crowd members were beyond what would be expected of an emotion recognition application for detecting faces of tennis players during a match. These were deemed unlikely to be necessary when attempting to find faces of players during tennis matches, and neglected during manual annotation.

@@

```{r accessories, fig.cap = "There are many more faces manually tagged as wearing glasses, and shows there was a more even split between those wearing headwear and those that were not.\\label{tab:accessories}"}

@@

ct<-CrossTable(table(ManFaces$glasses, ManFaces$visorhat), 
               prop.chisq = FALSE, 
               digits=max(2, getOption("digits")-2),
               expected = FALSE,
           prop.r = FALSE, prop.c = FALSE, prop.t = TRUE,
           drop.levels = TRUE, format = ("SPSS"), cell.layout = FALSE,
           dnn = c("Glasses","Visor/hat"))

pander(ct, caption = "Contingency table comparing the amount of captured faces of players that were wearing accessories.")
```

>>>>

\begin{table}[htp]
%\parbox{.5\linewidth}{
\caption{Counts of captures of different APIs against manually tagged faces.}
\label{tab:facecounts}
\centering
\begin{tabular}{ccccccc} \cline{1-3}\cline{5-7} 
\multicolumn{3}{c}{Animetrics}&&\multicolumn{3}{c}{Google}\\\cline{1-3}\cline{5-7}
Manual & Face & No Face & & Manual & Face & No Face\\ 
%heading
\cline{1-3}\cline{5-7} 
Face & 434 & 1861 & & Face & 1319 & 976\\
NoFace &527 & 787 & & NoFace &638 & 676 \\\cline{1-3}\cline{5-7}
\end{tabular}
\\[1.5ex]
\begin{tabular}{ccccccc}\\\cline{1-3}\cline{5-7} 
\multicolumn{3}{c}{Microsoft}&&\multicolumn{3}{c}{Skybiometry}\\
\cline{1-3}\cline{5-7}
Manual & Face & No Face & & Manual & Face & No Face\\ 
%heading
\cline{1-3}\cline{5-7} 
Face & 565 & 1730 & & Face & 493 & 1802\\
No Face &505 & 809 & & No Face &512 & 802 \\\cline{1-3}\cline{5-7}
\end{tabular}
\end{table}

Each table above considers the individual faces found in the set.
The upper left quadrant of tables shows the faces found manually and by each API. The ideal set would have majority of faces found belong to this category. 
Table \@ref(tab:facecounts), the comparison of Animetrics and Manually annotated faces, gives the lowest amount in this regard. Table \@ref(tab:facecounts), Google, found the largest amount of faces that matched those manually annotated.

Visual inspection showed that the `r amin %>% filter(type=="Google",!matchesManual) %>% nrow()` potential faces noted in Table \@ref(tab:facecounts), that were found by Google but not found manually were actually faces, however they were not all of players. Some of these crowd members were beyond what would be expected of an emotion recognition application for detecting faces of tennis players during a match. These were deemed unlikely to be necessary when attempting to find faces of players during tennis matches, and neglected during manual annotation.

@@

```{r accessories, eval=FALSE, fig.cap = "\\label{tab:accessories}"}

@@

prop.table(table(ManFaces$glasses, ManFaces$visorhat),1)
```

\begin{table}[ht]
\centering
%\parbox{.5\linewidth}{
\caption{Proprotions of faces captured manually tagged as wearing headwear given they wore glasses, or did not.}
\label{tab:accessories}
\begin{tabular}{ccc}
\hline 
 & Headwear & No Headwear\\ 
\hline
Glasses & 0.50 & 0.50 \\
No Glasses & 0.26 & 0.74 \\
\hline
\end{tabular}
\end{table}
